NSync: Boy bands meet nitrogen

### 2020-05-20 manuscript/manuscript.Rmd
skeleton mostly good

---
title: 'NSync: Boy bands meet nitrogen'
author:
- Hollister. J. W. ^\*^ *^1^*, Kellogg, D. Q. *^2^*, Arnold, C.*^3^*, Gold,
  A.*^2^*, Wilson, E. H.*^3^*, Chadwick, C.*^3^*, Dickson, D.*^3^*, Forshay, K.
  J.*^4^*
- *^1^* US Environmental Protection Agency, Office Of Research and Development,
  Atlantic Coastal Environmental Sciences Division, Narragansett, RI 02882
- *^2^* University of Rhode Island, Department of Natural Resources Science,
  Kingston, RI 02881
- *^3^* University of Connecticut, Center for Land Use Education and Research,
  Haddam, CT 06438
- *^4^* US Environmental Protection Agency, Office Of Research and Development,
  Groundwater Characterization and Remediation Division, Ada, OK 74820
- '^\*^ \*corresponding author: <hollister.jeff@epa.gov*>'
bibliography: manuscript.bib
output:
  word_document:
    reference_docx: manuscript_template.docx
editor_options:
  chunk_output_type: console
csl: ecology.csl
abstract: Great abstract goes here
---

@@

![Figure 1: Map of URI Watershed Watch lake and reservoir sampling sites](media/image1.jpg){width="5.7in" height="7.45in"}

`r fig_num("ww_map", caption = "Map of URI Watershed Watch lake and reservoir sampling sites")`

>>>>

---
title: 'NSync: Boy bands meet nitrogen'
author:
- |
  Hollister. J. W. ^\*^ *^1^*, Kellogg, D. Q. *^2^*, Arnold, C.*^3^*, Gold,
  A.*^2^*, Wilson, E. H.*^3^*, Chadwick, C.*^3^*, Dickson, D.*^3^*, Forshay, K.
  J.*^4^*
- |
  *^1^* US Environmental Protection Agency, Office Of Research and Development,
  Atlantic Coastal Environmental Sciences Division, Narragansett, RI 02882
- |
  *^2^* University of Rhode Island, Department of Natural Resources Science,
  Kingston, RI 02881
- |
  *^3^* University of Connecticut, Center for Land Use Education and Research,
  Haddam, CT 06438
- |
  *^4^* US Environmental Protection Agency, Office Of Research and Development,
  Groundwater Characterization and Remediation Division, Ada, OK 74820
- |
  '^\*^ \*corresponding author: <hollister.jeff@epa.gov*>'
bibliography: manuscript.bib
output:
  word_document:
    reference_docx: manuscript_template.docx
editor_options:
  chunk_output_type: console
csl: ecology.csl
abstract: Great abstract goes here
---

@@

![`r fig_num("ww_map", caption = "Map of URI Watershed Watch lake and reservoir sampling sites")`](../figures/ww_map.jpg){width="5.7in" height="7.45in"}
